### 2024-03-26 content/chapter_2.tex
:pencil: Update chapter 3

	\begin{subsection}{Wave Scattering Models}
		\begin{subsubsection}{Principles}
			\label{sc:principles}
			\gls{rf} wave can be manipulated by scattering elements made from \emph{programmable metamaterials} or \emph{passive antennas} \cite{Liang2022}.
			As discussed above, the former refracts or reflects the incident signals at the air-cell boundary and mainly applies a phase shift.
			In contrast, the latter allows the wave to feed into and collect from the antenna port such that some energy can be absorbed by the circuit and the rest is reradiated to the space.
			An interesting observation is that when excited by an external wave, a scattering element can simultaneously function as an object and a radiator.
			The corresponding scattered field is \cite{Hansen1989}
			\begin{equation}
				\vec{E}_\text{scatter}(Z_\mathrm{L}) = \underbrace{\vec{E}_\text{structural}}_\text{structural component} + \underbrace{\Gamma I_\mathrm{M} \vec{E}_\text{antenna}}_\text{antenna component},
			\end{equation}
			where $Z_\mathrm{L}$ is the load impedance, $\vec{E}_\text{structural}$ is the residual field under perfect matching (i.e., modelling as an object), $\vec{E}_\text{antenna}$ is the radiated field with unit current at the terminal and no external excitation (i.e., modelling as a radiator), $I_\mathrm{M}$ is the current under perfect matching, and $\Gamma$ is the reflection coefficient
			\begin{equation}
				\Gamma = \frac{Z_\mathrm{L} - Z_0^*}{Z_\mathrm{L} + Z_0},
				\label{eq:reflection_coefficient}
			\end{equation}
			and $Z_0$ is the characteristic impedance for programmable metamaterials or the input impedance for passive antennas.
			It is worth mentioning that
			\begin{itemize}
				\item \emph{Structural component:} Depends on the geometry and material of the scatterer. It is usually modelled as part of the environment multipath \cite{Thomas2012,Liang2020} or simply regarded a \gls{dc} offset when the impinging signal is \gls{cw} \cite{Boyer2014}.
				\item \emph{Antenna component:} Depends on the reflection coefficient that can be altered by load impedance. This is widely exploited for various scattering applications, such as backscatter modulation in \gls{bc} and passive beamforming in \gls{ris} \cite{Zhao2022a}.
			\end{itemize}
			We then introduce two canonical \gls{ris} models that will be adopted in the work chapters.
			More accurate models based on field equations (e.g., \cite{Ozdogan2020,Najafi2020}) and measurement fitting (e.g., \cite{Abeywickrama2020}) are also available in the literature.
			% physics-based (e.g., \cite{Ozdogan2020,Najafi2020}) and practical (e.g., \cite{Abeywickrama2020}) models
		\end{subsubsection}

		\begin{subsubsection}{Diagonal Phase Shift Model}
			A straightforward way to model the \gls{ris} scattering effect is to consider independent scattering elements with purely reactive load impedance \cite{Wu2018}.
			The reflection coefficient of the $n$-th element is thus
			\begin{equation}
				\theta_n = \frac{\jmath X_n - Z^*}{\jmath X_n + Z} = \exp(\jmath \phi_n),
			\end{equation}
			where $X_n$ is the reactance and $\phi_n$ is the phase shift on the scattered wave.
			For a total of $N_\mathrm{S}$ elements, the \gls{ris} scattering matrix is \emph{diagonal with complex unit-magnitude entries}
			\begin{equation}
				\mathbf{\Theta} = \mathrm{diag}(\theta_1, \ldots, \theta_{N_\mathrm{S}}) =
				\begin{bmatrix}
					\theta_1 & 0 & \cdots & 0 \\
					0 & \theta_2 & \cdots & 0 \\
					\vdots & \vdots & \ddots & \vdots \\
					0 & 0 & \cdots & \theta_{N_\mathrm{S}}
				\end{bmatrix}.
			\end{equation}
			Despite the strong assumptions, this diagonal phase shift model is widely used for the analysis of \gls{ris} systems due to its simplicity and analytical tractability.
		\end{subsubsection}

@@

		\begin{subsubsection}{Operation Regions and Signal Models}

@@

					P_\mathrm{DC}^\mathrm{R} = \eta_3 P_\mathrm{RF}^\mathrm{R} = \eta_3 \mathbb{E}\bigl\{ \lvert y(t) \rvert^2 \bigr\},

@@

					i_\mathrm{out} = \sum_{i=0}^\infty k_i R_\mathrm{A}^{i/2} \mathbb{E}\bigl\{ y^i(t) \bigr\} = \sum_{i=0,\text{even}}^\infty k_i R_\mathrm{A}^{i/2} \mathbb{E}\bigl\{ y^i(t) \bigr\}

@@

				where the second equality is because $\mathbb{E}\bigl\{y^i(t)\bigr\} = 0$ for odd $i$. Note that the dependency of $k_i$ on $-v_\mathrm{out}=-i_\mathrm{out} R_\mathrm{L}$ makes it nontrivial to formulate a closed-form expression for the harvested \gls{dc} power.

@@

					z \triangleq \sum_{i=2,\text{even}}^\infty \beta_i \mathbb{E}\bigl\{ y^i(t) \bigr\},

@@

				where $\beta_i = I_\mathrm{S} \frac{R_\mathrm{A}^{i/2}}{i!(n v_\mathrm{T})^i}$ is a constant. Truncating \eqref{eq:dc_power_nonlinear} at the second order yields the same result as \eqref{eq:dc_power_linear}, which suggests that the linear model is a special case of the more accurate non-linear model. For a moderate excitation, the contribution of higher-order terms is significant and should be modelled in the harvested \gls{dc} power.

@@

	\begin{subsection}{\glsfmtfull{r-e} Tradeoff}
		Despite \gls{wit} and \gls{wpt} share many similarities, their difference in design objectives, system architectures, and practical constraints make a joint implementation of \gls{swipt} particularly challenging.
		Some preference of \gls{wit} and \gls{wpt} are inherently conflicting, for example:
		\begin{itemize}
			\item \emph{Waveform and modulation:} Under an average power constraint, \gls{wit} favors Gaussian signaling with maximum entropy distribution \cite{Cover2005} while \gls{wpt} prefers deterministic (unmodulated) multisine with higher \gls{papr} \cite{Trotter2009}.
			\item \emph{Channel:} In a \gls{mimo} scenario, \gls{wit} favors full-rank \gls{nlos} with high spatial diversity while \gls{wpt} prefers rank-deficient \gls{los} with high spatial correlation \cite{Wu2022a}.
			\item \emph{Receiver:} The power sensitivity is usually in the range of -40 to -80 dBm for information receivers and -10 to -30 dBm for energy harvesters \cite{Lu2015}.
		\end{itemize}
		Those disparities translate to a fundamental tradeoff between information and power transfer in \gls{swipt} systems, which is often quantified by a \emph{\gls{r-e} region}.
		\begin{equation}
			\mathcal{C}_\mathrm{R-E}(P) \triangleq \Bigl\{ (r,e) : 0 \le r \le \log(1 + \gamma), \ 0 \le e \le z \Bigr\},
		\end{equation}
		where $P$ is the average transmit power, $\gamma$ is the \gls{snr} at the information decoder, and $z$ defined in \eqref{eq:dc_power_nonlinear} is uniquely mapped to the harvested \gls{dc} power.
		Each point in this region corresponds to a \emph{rate-energy pair} achieved by a particular \emph{resource allocation scheme}.
		It is worth mentioning that different transceive strategies (e.g., waveform and receiver design) can lead to totally different \gls{r-e} regions (instead of different points in the same region), which motivates a joint optimization of the transmitter, channel, and receiver.
	\end{subsection}

@@

		\begin{subsubsection}{Receiver Architectures}
			Figure \ref{fg:swipt_receiver_architectures} illustrates four potential architectures for a co-located \gls{swipt} receiver \cite{Clerckx2022}:
			\begin{figure}[H]
				\centering
				\subfloat[Ideal receiver]{
					\resizebox{0.6\columnwidth}{!}{
						\input{assets/chapter_2/receiver_ideal.tex}
					}
					\label{fg:receiver_ideal}
				}
				\\
				\subfloat[Time switching receiver]{
					\resizebox{0.6\columnwidth}{!}{
						\input{assets/chapter_2/receiver_ts.tex}
					}
					\label{fg:receiver_ts}
				}
				\\
				\subfloat[Power splitting receiver]{
					\resizebox{0.6\columnwidth}{!}{
						\input{assets/chapter_2/receiver_ps.tex}
					}
					\label{fg:receiver_ps}
				}
				\\
				\subfloat[Integrated receiver]{
					\resizebox{0.6\columnwidth}{!}{
						\input{assets/chapter_2/receiver_integrated.tex}
					}
					\label{fg:receiver_integrated}
				}
				\caption{
					Architectures of a co-located \gls{swipt} receiver.
				}
				\label{fg:swipt_receiver_architectures}
			\end{figure}

			\begin{itemize}
				\item \emph{Ideal receiver:} The received signal is used for both information decoding and energy harvesting. This is theoretically the most efficient design with a rectangle \gls{r-e} region but is unimplementable in practice due to hardware constraints.
				\item \emph{\gls{ts} receiver:} Each time frame is divided into individual \gls{wit} and \gls{wpt} phases, where the receiver switches between information decoder and energy harvester, respectively. The transmitted waveform and \gls{ris} response are optimized independently for each phase, and the resulting \gls{r-e} region is a triangle with two vertices corresponding to \gls{wit}-only and \gls{wpt}-only.
				\item \emph{\gls{ps} receiver:} The received signal is split into two parts with power ratio $\rho$ and $1{-}\rho$. The former is fed into the energy harvester and the latter is used for information decoding. The transmitter and \gls{ris} are jointly optimized for both purposes with the knowledge of splitting ratio, and the resulting \gls{r-e} region may be non-convex.
				\item \emph{Integrated receiver \cite{Kim2021a}:} The transmit signal is modulated in properties that can be well-preserved after rectification (e.g., pulse position) such that information can be decoded from the energy harvester output.
			\end{itemize}

@@

	\begin{subsection}{Modulation and Coding Schemes}
		\gls{bc} and \gls{ris} share the same wave scattering model in Section \ref{sc:principles}, but the reflection coefficient $\Gamma$ in \eqref{eq:reflection_coefficient} is exploited in different manners.
		The difference is two-fold:
		\begin{itemize}
			\item \emph{Modulation requires variation:} \gls{bc} relies on dynamically changing the reflection coefficient over time to encode information. This is different from \gls{ris} where the optimal configuration (and reflection coefficient) is fixed for a given channel realization.
			\item \emph{Harvesting requires absorption:} Part of the impinging wave should be fed into the node to power its operation. This is different from \gls{ris} where a full reflection is desired to maximize its channel control capability.
		\end{itemize}
		Denote the amplitude scattering ratio of the \gls{bc} node as $\alpha$, i.e., the power absorption ratio is $(1-\alpha)^2$. Some popular modulation schemes are summarized below:
		\begin{itemize}
			\item \emph{\gls{qam} \cite{Thomas2012a}:} The reflection coefficient corresponding to the $m$-th symbol is
			\begin{equation}
				\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert}
			\end{equation}
			where $c_m$ is the corresponding constellation point.
			This scheme is simple but exhibits a low detection \gls{snr} especially when the constellation size is large.
			\item \emph{\gls{fsk} \cite{Abbasi2021a}:} For 2-\gls{fsk}, the reflection coefficient is
			\begin{equation}
				\Gamma(t) =
				\begin{cases}
					\alpha, & t \in \bigl[\frac{n}{\Delta f},\frac{2n+1}{2 \Delta f}\bigr) \\
					-\alpha, & t \in \bigl[\frac{2n+1}{2 \Delta f},\frac{n+1}{\Delta f}\bigr)
				\end{cases}
				= \frac{\pi}{4} \sum_{m=1,\text{odd}}^\infty \frac{1}{m} \sin\bigl(2\pi m \Delta f t\bigr),
			\end{equation}
			where $n \in \mathbb{N}$.
			If the incident wave is a \gls{cw} at frequency $f_0$, the reflected signal is dominated by its first harmonic
			% \begin{equation}
			% 	y(t) = \sum_{m=1,\text{odd}}^\infty \frac{\pi}{4m} \cos(2 \pi f_0 t) \sin\bigl(2\pi m \Delta f t\bigr),
			% \end{equation}
			\begin{equation}
				s_1(t) = \frac{\pi}{2} \Bigl(\sin\bigl(2 \pi (f_0 {+} \Delta f) t\bigr) - \sin\bigl(2 \pi (f_0 {-} \Delta f) t\bigr)\Bigr).
			\end{equation}
			That is, periodically switching the reflection coefficient at rate $\Delta f$ results in a frequency shift $\pm \Delta f$ on the reflected signal.
			Practical implementations have been demonstrated on a variety of license-free protocols (e.g., HitchHike \cite{Zhang2016a}, Inter-Technology \cite{Iyer2016}, Passive Wi-Fi \cite{Kellogg2017}, \gls{ble}-Backscatter \cite{Ensworth2017}) where the mirror copy can be suppressed.
			\item \emph{\gls{css} \cite{Talla2017}:} A chirp is a signal whose frequency increases or decreases over time.
			\gls{css} uses wideband linear-frequency modulated chirps to encode information, which is from \gls{dsss} and \gls{fsss} with pseudo-random sequences and \gls{fsk} with discrete frequencies.
			In particular, $N+1$ reflection coefficients of the same envelope are sequentially selected at a regular rate $\Delta f$, given by
			\begin{equation}
				\Gamma_n = \alpha \exp(\jmath \phi_n), \quad n \in \{0, 1, \ldots, N\},
			\end{equation}
			where $\phi_n = \frac{2 \pi}{\Delta f}(A n^2 + B n)$ and $A$, $B$ are constants.
			As the core modulation scheme in \gls{lora}, it is more robust to noise and interference (with a reception sensitivity of -149 dBm), harder to be detected by eavesdroppers, and can be used for ranging and localization \cite{Abbasi2021a}.

>>>>

	\begin{subsection}{Wave Scattering Models}
		\begin{subsubsection}{Principles}\label{sc:principles}
			\gls{rf} wave can be manipulated by scattering elements made from \emph{programmable metamaterials} or \emph{passive antennas} \cite{Liang2022}.
			As discussed above, the former refracts or reflects the incident signals at the air-cell boundary and mainly applies a phase shift.
			In contrast, the latter allows the wave to feed into and collect from the antenna port such that some energy can be absorbed by the circuit and the rest is reradiated to the space.
			An interesting observation is that when excited by an external wave, a scattering element can simultaneously function as an object and a radiator.
			The corresponding scattered field is \cite{Hansen1989}
			\begin{equation}
				\vec{E}_\text{scatter}(Z_\mathrm{L}) = \underbrace{\vec{E}_\text{structural}}_\text{structural component} + \underbrace{\Gamma I_\mathrm{M} \vec{E}_\text{antenna}}_\text{antenna component},
			\end{equation}
			where $Z_\mathrm{L}$ is the load impedance, $\vec{E}_\text{structural}$ is the residual field under perfect matching (i.e., modelling as an object), $\vec{E}_\text{antenna}$ is the radiated field with unit current at the terminal and no external excitation (i.e., modelling as a radiator), $I_\mathrm{M}$ is the current under perfect matching, and $\Gamma$ is the reflection coefficient
			\begin{equation}
				\Gamma = \frac{Z_\mathrm{L} - Z_0^*}{Z_\mathrm{L} + Z_0},
				\label{eq:reflection_coefficient}
			\end{equation}
			and $Z_0$ is the characteristic impedance for programmable metamaterials or the input impedance for passive antennas.
			It is worth mentioning that
			\begin{itemize}
				\item \emph{Structural component:} Depends on the geometry and material of the scatterer. It is usually modelled as part of the environment multipath \cite{Thomas2012,Liang2020} or simply regarded a \gls{dc} offset when the impinging signal is \gls{cw} \cite{Boyer2014}.
				\item \emph{Antenna component:} Depends on the reflection coefficient that can be altered by load impedance. This is widely exploited for various scattering applications, such as backscatter modulation in \gls{bc} and passive beamforming in \gls{ris} \cite{Zhao2022a}.
			\end{itemize}
			We then introduce two canonical \gls{ris} models that will be adopted in the work chapters.
			More accurate models based on field equations (e.g., \cite{Ozdogan2020,Najafi2020}) and measurement fitting (e.g., \cite{Abeywickrama2020}) are also available in the literature.
			% physics-based (e.g., \cite{Ozdogan2020,Najafi2020}) and practical (e.g., \cite{Abeywickrama2020}) models
		\end{subsubsection}

		\begin{subsubsection}{Diagonal Phase Shift Model}
			A straightforward way to model the \gls{ris} scattering effect is to consider independent scattering elements with purely reactive load impedance \cite{Wu2018}.
			The reflection coefficient of the $n$-th element is thus
			\begin{equation}
				\theta_n = \frac{\jmath X_n - Z^*}{\jmath X_n + Z} = \exp(\jmath \phi_n),
				\label{eq:reflection_coefficient_ris}
			\end{equation}
			where $X_n$ is the reactance and $\phi_n$ is the phase shift on the scattered wave.
			For a total of $N_\mathrm{S}$ elements, the \gls{ris} scattering matrix is \emph{diagonal with complex unit-magnitude entries}
			\begin{equation}
				\mathbf{\Theta} = \mathrm{diag}(\theta_1, \ldots, \theta_{N_\mathrm{S}}) =
				\begin{bmatrix}
					\theta_1 & 0 & \cdots & 0 \\
					0 & \theta_2 & \cdots & 0 \\
					\vdots & \vdots & \ddots & \vdots \\
					0 & 0 & \cdots & \theta_{N_\mathrm{S}}
				\end{bmatrix}.
			\end{equation}
			Despite the strong assumptions, this diagonal phase shift model is widely used for the analysis of \gls{ris} systems due to its simplicity and analytical tractability.
		\end{subsubsection}

@@

		\begin{subsubsection}{Operation Regions and Signal Models}\label{sc:operation_regions}

@@

					P_\mathrm{DC}^\mathrm{R} = \eta_3 P_\mathrm{RF}^\mathrm{R} = \eta_3 \mathbb{A}\bigl\{ \lvert y(t) \rvert^2 \bigr\},

@@

					i_\mathrm{out} = \sum_{i=0}^\infty k_i R_\mathrm{A}^{i/2} \mathbb{A}\bigl\{ y^i(t) \bigr\} = \sum_{i=0,\text{even}}^\infty k_i R_\mathrm{A}^{i/2} \mathbb{A}\bigl\{ y^i(t) \bigr\}

@@

				where the second equality is because $\mathbb{A}\bigl\{y^i(t)\bigr\} = 0$ for odd $i$. Note that the dependency of $k_i$ on $-v_\mathrm{out}=-i_\mathrm{out} R_\mathrm{L}$ makes it nontrivial to formulate a closed-form expression for the harvested \gls{dc} power.

@@

					z \triangleq \sum_{i=2,\text{even}}^{n_0} \beta_i \mathbb{A}\bigl\{ y^i(t) \bigr\},

@@

				where $\beta_i = I_\mathrm{S} \frac{R_\mathrm{A}^{i/2}}{i!(n v_\mathrm{T})^i}$ is a constant and $n_0$ is the truncation order. Selecting $n_0=2$ yields the same result as \eqref{eq:dc_power_linear}, which suggests that the linear model is a special case of the more accurate non-linear model. For a moderate excitation, the contribution of higher-order terms is significant and should be modelled in the harvested \gls{dc} power.

@@

	\begin{subsection}{\glsfmtfull{r-e} Tradeoff}
		Despite \gls{wit} and \gls{wpt} share many similarities, their difference in design objectives, system architectures, and practical constraints make a joint implementation of \gls{swipt} particularly challenging.
		Some preference of \gls{wit} and \gls{wpt} are inherently conflicting, for example:
		\begin{itemize}
			\item \emph{Waveform and modulation:} Under an average power constraint, \gls{wit} favors Gaussian signaling with maximum entropy distribution \cite{Cover2005} while \gls{wpt} prefers deterministic (unmodulated) multisine with higher \gls{papr} \cite{Trotter2009}.
			\item \emph{Channel:} In a \gls{mimo} scenario, \gls{wit} favors full-rank \gls{nlos} with high spatial diversity while \gls{wpt} prefers rank-deficient \gls{los} with high spatial correlation \cite{Wu2022a}.
			\item \emph{Receiver:} The power sensitivity is usually in the range of -40 to -80 dBm for information receivers and -10 to -30 dBm for energy harvesters \cite{Lu2015}.
		\end{itemize}
		Those disparities translate to a fundamental trade-off between information and power transfer in \gls{swipt} systems, which is often quantified by a \emph{\gls{r-e} region}.
		\begin{equation}
			\mathcal{C}_\mathrm{R-E}(P) \triangleq \Bigl\{ (r,e) : 0 \le r \le \log(1 + \gamma), \ 0 \le e \le z \Bigr\},
		\end{equation}
		where $P$ is the average transmit power, $\gamma$ is the \gls{snr} at the information decoder, and $z$ defined in \eqref{eq:dc_power_nonlinear} is uniquely mapped to the harvested \gls{dc} power.
		Each point in this region corresponds to a \emph{rate-energy pair} achieved by a particular \emph{resource allocation scheme}.
		It is worth mentioning that different transceive strategies (e.g., waveform and receiver design) can lead to totally different \gls{r-e} regions (instead of different points in the same region), which motivates a joint optimization of the transmitter, channel, and receiver.
	\end{subsection}

@@

		\begin{subsubsection}{Receiver Architectures}\label{sc:receiver_architectures}
			Figure \ref{fg:swipt_receiver_architectures} illustrates four potential architectures for a co-located \gls{swipt} receiver \cite{Clerckx2022}:
			\begin{figure}[H]
				\centering
				\subfloat[Ideal receiver]{
					\resizebox{0.6\columnwidth}{!}{
						\input{assets/chapter_2/receiver_ideal.tex}
					}
					\label{fg:receiver_ideal}
				}
				\\
				\subfloat[Time switching receiver]{
					\resizebox{0.6\columnwidth}{!}{
						\input{assets/chapter_2/receiver_ts.tex}
					}
					\label{fg:receiver_ts}
				}
				\\
				\subfloat[Power splitting receiver]{
					\resizebox{0.6\columnwidth}{!}{
						\input{assets/chapter_2/receiver_ps.tex}
					}
					\label{fg:receiver_ps}
				}
				\\
				\subfloat[Integrated receiver]{
					\resizebox{0.6\columnwidth}{!}{
						\input{assets/chapter_2/receiver_integrated.tex}
					}
					\label{fg:receiver_integrated}
				}
				\caption{
					Architectures of a co-located \gls{swipt} receiver.
				}
				\label{fg:swipt_receiver_architectures}
			\end{figure}

			\begin{itemize}
				\item \emph{Ideal receiver:} The received signal is used for both information decoding and energy harvesting. This is theoretically the most efficient design with a rectangle \gls{r-e} region but is unimplementable in practice due to hardware constraints.
				\item \emph{\gls{ts} receiver:} Each time block is divided into individual \gls{wit} and \gls{wpt} phases, where the receiver switches between information decoder and energy harvester, respectively. The transmitted waveform and \gls{ris} response are optimized independently for each phase, and the resulting \gls{r-e} region is a triangle with two vertices corresponding to \gls{wit}-only and \gls{wpt}-only.
				\item \emph{\gls{ps} receiver:} The received signal is split into two parts with power ratio $\rho$ and $1{-}\rho$. The former is fed into the energy harvester and the latter is used for information decoding. The transmitter and \gls{ris} are jointly optimized for both purposes with the knowledge of splitting ratio, and the resulting \gls{r-e} region may be non-convex.
				\item \emph{Integrated receiver \cite{Kim2021a}:} The transmit signal is modulated in properties that can be well-preserved after rectification (e.g., pulse position) such that information can be decoded from the energy harvester output.
			\end{itemize}

@@

	\begin{subsection}{Modulation and Coding Schemes}
		\gls{bc} and \gls{ris} share the same wave scattering model in Section \ref{sc:principles}, but the reflection coefficient $\Gamma$ in \eqref{eq:reflection_coefficient} is exploited in different manners.
		The difference is two-fold:
		\begin{itemize}
			\item \emph{Modulation requires variation:} \gls{bc} relies on dynamically changing the reflection coefficient over time to encode information. This is different from \gls{ris} where the optimal configuration (and reflection coefficient) is fixed for a given channel realization.
			\item \emph{Harvesting requires absorption:} Part of the impinging wave should be fed into the node to power its operation. This is different from \gls{ris} where a full reflection is desired to maximize its channel control capability.
		\end{itemize}
		Denote the amplitude scattering ratio of the \gls{bc} node as $\alpha$, i.e., the power absorption ratio is $(1-\alpha)^2$. Some popular modulation schemes are summarized below:
		\begin{itemize}
			\item \emph{\gls{qam} \cite{Thomas2012a}:} The reflection coefficient corresponding to the $m$-th symbol is
			\begin{equation}
				\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert}
			\end{equation}
			where $c_m$ is the corresponding constellation point.
			This scheme is simple but exhibits a low detection \gls{snr} especially when the constellation size is large.
			\item \emph{\gls{fsk} \cite{Abbasi2021a}:} For 2-\gls{fsk}, the reflection coefficient is
			\begin{equation}
				\Gamma(t) =
				\begin{cases}
					\alpha, & t \in \bigl[\frac{n}{\Delta f},\frac{2n+1}{2 \Delta f}\bigr) \\
					-\alpha, & t \in \bigl[\frac{2n+1}{2 \Delta f},\frac{n+1}{\Delta f}\bigr)
				\end{cases}
				= \frac{\pi}{4} \sum_{m=1,\text{odd}}^\infty \frac{\alpha}{m} \sin\bigl(2\pi m \Delta f t\bigr),
			\end{equation}
			where $n \in \mathbb{N}$.
			If the incident wave is a \gls{cw} at frequency $f_0$, the reflected signal is dominated by its first harmonic
			% \begin{equation}
			% 	y(t) = \sum_{m=1,\text{odd}}^\infty \frac{\pi}{4m} \cos(2 \pi f_0 t) \sin\bigl(2\pi m \Delta f t\bigr),
			% \end{equation}
			\begin{equation}
				s_1(t) = \frac{\alpha \pi}{2} \Bigl(\sin\bigl(2 \pi (f_0 {+} \Delta f) t\bigr) - \sin\bigl(2 \pi (f_0 {-} \Delta f) t\bigr)\Bigr).
			\end{equation}
			That is, periodically switching the reflection coefficient at rate $\Delta f$ results in a frequency shift $\pm \Delta f$ on the reflected signal.
			Practical implementations have been demonstrated on a variety of license-free protocols (e.g., HitchHike \cite{Zhang2016a}, Inter-Technology \cite{Iyer2016}, Passive Wi-Fi \cite{Kellogg2017}, \gls{ble}-Backscatter \cite{Ensworth2017}) where the mirror copy can be suppressed.
			\item \emph{\gls{css} \cite{Talla2017}:} A chirp is a signal whose frequency increases or decreases over time.
			\gls{css} uses wideband linear-frequency modulated chirps to encode information, which is from \gls{dsss} and \gls{fsss} with pseudo-random sequences and \gls{fsk} with discrete frequencies.
			In particular, $N+1$ reflection coefficients of the same envelope are sequentially selected at a regular rate $\Delta f$, given by
			\begin{equation}
				\Gamma_n = \alpha \exp(\jmath \phi_n), \quad n \in \{0, 1, \ldots, N\},
			\end{equation}
			where $\phi_n = \frac{2 \pi}{\Delta f}(A n^2 + B n)$ and $A$, $B$ are constants.
			As the core modulation scheme in \gls{lora}, it is more robust to noise and interference (with a reception sensitivity of -149 dBm), harder to be detected by eavesdroppers, and can be used for ranging and localization \cite{Abbasi2021a}.
